%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Long Lined Cover Letter
% LaTeX Template
% Version 1.0 (1/6/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Matthew J. Miller
% http://www.matthewjmiller.net/howtos/customized-cover-letter-scripts/
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[10pt,stdletter,dateno,sigleft]{newlfm} % Extra options: 'sigleft' for a left-aligned signature, 'stdletternofrom' to remove the from address, 'letterpaper' for US letter paper - consult the newlfm class manual for more options

\usepackage{charter} % Use the Charter font for the document text



\newlfmP{sigsize=50pt} % Slightly decrease the height of the signature field
\newlfmP{addrfromphone} % Print a phone number under the sender's address
\newlfmP{addrfromemail} % Print an email address under the sender's address
\PhrPhone{Phone} % Customize the "Telephone" text
\PhrEmail{Email} % Customize the "E-mail" text



%----------------------------------------------------------------------------------------
%	YOUR NAME AND CONTACT INFORMATION
%----------------------------------------------------------------------------------------

\namefrom{Brandon Fung} % Name

\addrfrom{
\today\\[12pt] % Date
55 Milos Rd \\ % Address
Richmond Hill, Ontario L4E 0S9
}

\phonefrom{(226) 989-3038} % Phone number

\emailfrom{b6fung@uwaterloo.ca} % Email address

%----------------------------------------------------------------------------------------
%	ADDRESSEE AND GREETING/CLOSING
%----------------------------------------------------------------------------------------

\greetto{Dear Sir or Madam} % Greeting text
\closeline{Sincerely yours,} % Closing text

\nameto{} % Addressee of the letter above the to address

\addrto{
COMPANY\\
}

%----------------------------------------------------------------------------------------

\begin{document}
\begin{newlfm}

%----------------------------------------------------------------------------------------
%	LETTER CONTENT
%----------------------------------------------------------------------------------------

I am writing this cover letter to apply for an 8 month internship at COMPANY for the position of 
POSITION, for the term starting from May 2015 to December 2015.  Enclosed is my resume and other 
items that have been provided by the University of Waterloo.

The position POSITION would be suited for me because of my previous experience at other technology companies and small brief side projects that were completed on the side. One such example was the time at Palantir Technologies in which I was given the title of Product Quality Engineer.  My responsibilities were to test different cases of the product and also to write testing automation for the product.  This automation was written in java and was using a selenium framework to do the front end testing of the product.  I was also responsible for the end to end testing by writing on top of current automation to suit it to what was needed.

Another example would be a mini project that was completed at the Calhacks hackathon in which me and another student from Waterloo created a way to visualize data and manipulate it using the Leap Motion and displaying the data on Unity.  The code was written in C\# and was awarded the Meraki Presence Analytics Award.

I hope that you could give me a chance to interview for the position and I wish to thank you for considering me for POSITION.

%----------------------------------------------------------------------------------------

\end{newlfm}
\end{document}
